---
title: "Final Analysis"
author: "Team MEAD"
date: "2025-01-31"
output: pdf_document
---

### Load Libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(data.table)
library(dplyr)
library(tidyverse)
library(haven)
library(survey)
library(haven)
library(knitr)
library(car)
```

### Load Data from Combined Mental and BP
```{r}
BP_MEN_Merge <- readRDS("BP_MEN_MERGE.rds")

```

## Data Cleaning


### Mental Illness Scoring and Categories

Scoring based off References as noted in the codebook:

+ Kroenke K, Spitzer RL, William JB. The PHQ-9: validity of a brief depression severity measure. J Gen Intern Med 2001; 16: 1606-13.

+ Kroenke K, Spitzer RL. The PHQ-9: a new depression and diagnostic severity measure. Psych Annals 2002; 32:509-21.

+ Spitzer RL, Kroenke K, Williams JB. Validation and utility of a self-report version of Prime MD: the PHQ primary care study. JAMA 1999; 282: 1737-44.

Of note, within the first paper, scores are associated as follows:

a PHQ-9 score > or =10 had a sensitivity of 88% and a specificity of 88% for major depression. PHQ-9 scores of 5, 10, 15, and 20 represented mild, moderate, moderately severe, and severe depression, respectively. Results were similar in the primary care and obstetrics-gynecology samples.

### Total Score per person

Of note, data from 2021-2023 was not included in the merged data from MEN and BP
```{r}
# Clean up the scores to recode 7 & 9 score from NHANES data to "NA"
BP_MEN_Merge$DPQ010 <- replace(BP_MEN_Merge$DPQ010, BP_MEN_Merge$DPQ010 == 7, NA)
BP_MEN_Merge$DPQ010 <- replace(BP_MEN_Merge$DPQ010, BP_MEN_Merge$DPQ010 == 9, NA)  

BP_MEN_Merge$DPQ020 <- replace(BP_MEN_Merge$DPQ020, BP_MEN_Merge$DPQ020 == 7, NA)
BP_MEN_Merge$DPQ020 <- replace(BP_MEN_Merge$DPQ020, BP_MEN_Merge$DPQ020 == 9, NA)  

BP_MEN_Merge$DPQ030 <- replace(BP_MEN_Merge$DPQ030, BP_MEN_Merge$DPQ030 == 7, NA)
BP_MEN_Merge$DPQ030 <- replace(BP_MEN_Merge$DPQ030, BP_MEN_Merge$DPQ030 == 9, NA)  

BP_MEN_Merge$DPQ040 <- replace(BP_MEN_Merge$DPQ040, BP_MEN_Merge$DPQ040 == 7, NA)
BP_MEN_Merge$DPQ040 <- replace(BP_MEN_Merge$DPQ040, BP_MEN_Merge$DPQ040 == 9, NA)  

BP_MEN_Merge$DPQ050 <- replace(BP_MEN_Merge$DPQ050, BP_MEN_Merge$DPQ050 == 7, NA)
BP_MEN_Merge$DPQ050 <- replace(BP_MEN_Merge$DPQ050, BP_MEN_Merge$DPQ050 == 9, NA)  

BP_MEN_Merge$DPQ060 <- replace(BP_MEN_Merge$DPQ060, BP_MEN_Merge$DPQ060 == 7, NA)
BP_MEN_Merge$DPQ060 <- replace(BP_MEN_Merge$DPQ060, BP_MEN_Merge$DPQ060 == 9, NA)  

BP_MEN_Merge$DPQ070 <- replace(BP_MEN_Merge$DPQ070, BP_MEN_Merge$DPQ070 == 7, NA)
BP_MEN_Merge$DPQ070 <- replace(BP_MEN_Merge$DPQ070, BP_MEN_Merge$DPQ070 == 9, NA)  

BP_MEN_Merge$DPQ080 <- replace(BP_MEN_Merge$DPQ080, BP_MEN_Merge$DPQ080 == 7, NA)
BP_MEN_Merge$DPQ080 <- replace(BP_MEN_Merge$DPQ080, BP_MEN_Merge$DPQ080 == 9, NA)  

BP_MEN_Merge$DPQ090 <- replace(BP_MEN_Merge$DPQ090, BP_MEN_Merge$DPQ090 == 7, NA)
BP_MEN_Merge$DPQ090 <- replace(BP_MEN_Merge$DPQ090, BP_MEN_Merge$DPQ090 == 9, NA)  

BP_MEN_Merge$DPQ100 <- replace(BP_MEN_Merge$DPQ100, BP_MEN_Merge$DPQ100 == 7, NA)
BP_MEN_Merge$DPQ100 <- replace(BP_MEN_Merge$DPQ100,BP_MEN_Merge$DPQ100 == 9, NA)  

Clean_BP_MEN_Merge <- BP_MEN_Merge
## Table to see the variables present

# table(Clean_MEN_MERGED_NHANES$DPQ010)
# table(Clean_MEN_MERGED_NHANES$DPQ020)
# table(Clean_MEN_MERGED_NHANES$DPQ030)
# table(Clean_MEN_MERGED_NHANES$DPQ040)
# table(Clean_MEN_MERGED_NHANES$DPQ050)
# table(Clean_MEN_MERGED_NHANES$DPQ060)
# table(Clean_MEN_MERGED_NHANES$DPQ070)
# table(Clean_MEN_MERGED_NHANES$DPQ080)
# table(Clean_MEN_MERGED_NHANES$DPQ090)
# table(Clean_MEN_MERGED_NHANES$DPQ100)


Total_Score_MEN_NHANES <- Clean_BP_MEN_Merge %>% 
  mutate(Total_Score = rowSums(across(c(DPQ010, DPQ020, DPQ030, DPQ040, DPQ050, DPQ060, DPQ070, DPQ080, DPQ090)), na.rm = TRUE)) %>% 
  mutate(Category = case_when(
    Total_Score < 5  ~ "None",
    Total_Score >= 5 & Total_Score < 10  ~ "Mild",
    Total_Score >= 10 & Total_Score < 15  ~ "Moderate",
    Total_Score >= 15 & Total_Score < 20  ~ "Moderately Severe",
    Total_Score >= 20  ~ "Severe"))

### 2013 - 2014 Data

MEN_Counts_2013_2014 <- tibble("None" = sum(Total_Score_MEN_NHANES$Category == "None" & Total_Score_MEN_NHANES$Survey_Cycle == "2013-2014"),
                               "Mild" = sum(Total_Score_MEN_NHANES$Category == "Mild" & Total_Score_MEN_NHANES$Survey_Cycle == "2013-2014"),
                               "Moderate" = sum(Total_Score_MEN_NHANES$Category == "Moderate" & Total_Score_MEN_NHANES$Survey_Cycle == "2013-2014"),
                               "Moderately Severe" = sum(Total_Score_MEN_NHANES$Category == "Moderately Severe" & Total_Score_MEN_NHANES$Survey_Cycle == "2013-2014"),
                               "Severe" = sum(Total_Score_MEN_NHANES$Category == "Severe" & Total_Score_MEN_NHANES$Survey_Cycle == "2013-2014"))

### 2015_2016


MEN_Counts_2015_2016 <- tibble("None" = sum(Total_Score_MEN_NHANES$Category == "None" & Total_Score_MEN_NHANES$Survey_Cycle == "2015-2016"),
                               "Mild" = sum(Total_Score_MEN_NHANES$Category == "Mild" & Total_Score_MEN_NHANES$Survey_Cycle == "2015-2016"),
                               "Moderate" = sum(Total_Score_MEN_NHANES$Category == "Moderate" & Total_Score_MEN_NHANES$Survey_Cycle == "2015-2016"),
                               "Moderately Severe" = sum(Total_Score_MEN_NHANES$Category == "Moderately Severe" & Total_Score_MEN_NHANES$Survey_Cycle == "2015-2016"),
                               "Severe" = sum(Total_Score_MEN_NHANES$Category == "Severe" & Total_Score_MEN_NHANES$Survey_Cycle == "2015-2016"))

### 2017 - 2020

MEN_Counts_2017_2020 <- tibble("None" = sum(Total_Score_MEN_NHANES$Category == "None" & Total_Score_MEN_NHANES$Survey_Cycle == "2017-2020"),
                               "Mild" = sum(Total_Score_MEN_NHANES$Category == "Mild" & Total_Score_MEN_NHANES$Survey_Cycle == "2017-2020"),
                               "Moderate" = sum(Total_Score_MEN_NHANES$Category == "Moderate" & Total_Score_MEN_NHANES$Survey_Cycle == "2017-2020"),
                               "Moderately Severe" = sum(Total_Score_MEN_NHANES$Category == "Moderately Severe" & Total_Score_MEN_NHANES$Survey_Cycle == "2017-2020"),
                               "Severe" = sum(Total_Score_MEN_NHANES$Category == "Severe" & Total_Score_MEN_NHANES$Survey_Cycle == "2017-2020"))

### 2021 - 2023

MEN_Counts_2021_2023 <- tibble("None" = sum(Total_Score_MEN_NHANES$Category == "None" & Total_Score_MEN_NHANES$Survey_Cycle == "2021-2023"),
                               "Mild" = sum(Total_Score_MEN_NHANES$Category == "Mild" & Total_Score_MEN_NHANES$Survey_Cycle == "2021-2023"),
                               "Moderate" = sum(Total_Score_MEN_NHANES$Category == "Moderate" & Total_Score_MEN_NHANES$Survey_Cycle == "2021-2023"),
                               "Moderately Severe" = sum(Total_Score_MEN_NHANES$Category == "Moderately Severe" & Total_Score_MEN_NHANES$Survey_Cycle == "2021-2023"),
                               "Severe" = sum(Total_Score_MEN_NHANES$Category == "Severe" & Total_Score_MEN_NHANES$Survey_Cycle == "2021-2023"))


MEN_Counts_Total <- rbind(MEN_Counts_2013_2014,
                          MEN_Counts_2015_2016,
                          MEN_Counts_2017_2020,
                          MEN_Counts_2021_2023)

MEN_year <- c("2013-2014", "2015-2016", "2017-2020", "2021-2023")

MEN_Counts_Total <- cbind(MEN_year, MEN_Counts_Total)

MEN_Counts_Total
```

## Data Set Clean Up
Variables kept are demographic variables, bp control, and cc variables.

Variables include: 
+ svy_id 
+ svy_year 
+ demo_age_cat – age category (years)
+ demo_race – race/ethnicty
+ demo_race_black – black, yes/no
+ demo_gender – gender 
+ bp_uncontrolled_accaha -- uncontrolled BP defined by 2017 ACC/AHA
+ htn_accaha -  Hypertension defined by the 2017 ACC/AHA BP guideline
+ cc_smoke – smoking status 
+ cc_bmi -- BMI 
+ cc_diabetes – prevalent diabetes 
+ cc_ckd – prevalent chronic kidney disease

```{r}
# View(BP_MEN_Merge)
```

## Select BP and Depression Variables
```{r}

BP_MEN_draft <- Total_Score_MEN_NHANES %>% 
  dplyr::select(svy_id, svy_year, svy_weight_mec, svy_psu, svy_strata, demo_age_cat, demo_race,
         demo_race_black, demo_gender, bp_uncontrolled_accaha, 
         htn_accaha, cc_smoke, cc_bmi, cc_diabetes, cc_ckd,
         Total_Score, Category)
BP_MEN_draft$Category <- factor(BP_MEN_draft$Category, 
                                 levels = c("None", "Mild", "Moderate", 
                                            "Moderately Severe", "Severe"))

# View(BP_MEN_draft)
```

## Merge NHANES Prescription Medication Data
```{r}
## Find the antidepressant drugs and their codes from the codebook data frame

drug_codes <- read_xpt("RXQ_DRUG.xpt")
#View(drug_codes)

#filter only for antidepressant drug codes
drug_codes_filter <- drug_codes %>% 
  filter(RXDDCN1B == "ANTIDEPRESSANTS") %>% 
  dplyr::select(RXDDRGID)
# View(drug_codes_filter)

#print(drug_codes_filter)

### Import Prescription Medication Survey Data from 2013-2014, 2015-2016, and 2017-2020

RXQ_drug_survey_2013_2014 <- read_xpt("RXQ_RX_H_2013_2014.xpt")
# View(RXQ_drug_survey_2013_2014)

RXQ_drug_survey_2015_2016 <- read_xpt("RXQ_RX_I_2015_2016.xpt")
# View(RXQ_drug_survey_2015_2016)

RXQ_drug_survey_2017_2020 <- read_xpt("P_RXQ_RX_2017_2020.xpt")
# View(RXQ_drug_survey_2017_2020)

### Create a svy_year column that annotates which year the survey was from


RXQ_drug_survey_2013_2020 <- rbind(RXQ_drug_survey_2013_2014, RXQ_drug_survey_2015_2016, RXQ_drug_survey_2017_2020)

#View(RXQ_drug_survey_2013_2020)


## Dummy Code new variable name 'Antidepressants'. If the respondent is on any of the 'antidepressants' listed from the code book, they receive a value of 1. If they are not, they receive a value of 0.

RXQ_drug_survey_2013_2020_dummy_code <- RXQ_drug_survey_2013_2020 %>%
  filter(!is.na(RXDDRGID)) %>% 
  mutate(Antidepressants = ifelse(RXDDRGID %in% c("a70010", "c00249", "c00250", "d00144",
                                                  "d00145", "d00146",  "d00236", "d00259",
                                                  "d00395", "d00873", "d00874", "d00875",
                                                  "d00876", "d00877", "d00880", "d00882",
                                                  "d00883", "d00884", "d03157", "d03181",
                                                  "d03804", "d03808", "d04025", "d04332",
                                                  "d04812", "d05355", "d06635", "d07113",
                                                  "d07740", "d08114", "d08125", "h00035")
                                  , "Yes", "No")) %>% 
  relocate(Antidepressants, .after = 2) %>% 
  rename(svy_id = SEQN)
  
# View(RXQ_drug_survey_2013_2020_dummy_code)
```


```{r}
RXQ_drug_survey_2013_2020_dummy_code_filtered <- RXQ_drug_survey_2013_2020_dummy_code %>% 
  mutate(Antidepressant_Y_N = "Yes") %>% 
  group_by(svy_id) %>%
  summarize(Antidepressant_Y_N = ifelse(any(Antidepressants == "Yes"), Antidepressant_Y_N[Antidepressants == "Yes"][1], "No"), .groups = "drop")

# View(RXQ_drug_survey_2013_2020_dummy_code_filtered)
```


## Full join of prescription and mental health/BP data
```{r}
BP_MEN_Select <- inner_join(BP_MEN_draft, RXQ_drug_survey_2013_2020_dummy_code_filtered, by = "svy_id")

# View(BP_MEN_Select)
```

## Filtering for Hypertensive Individuals and Creating Variables for Survey Design
```{r}
unfiltered_df <- BP_MEN_Select
BP_MEN_Select <- BP_MEN_Select %>% 
  filter(htn_accaha == "Yes")
#Survey design for regression
nhanesDesignUnfiltered <- svydesign(id = ~svy_psu,  
                          strata  = ~svy_strata, 
                          weights = ~svy_weight_mec,   
                          nest    = TRUE,      
                          data    = unfiltered_df)

nhanesDesignSelect <- svydesign(id = ~svy_psu,  
                          strata  = ~svy_strata, 
                          weights = ~svy_weight_mec,   
                          nest    = TRUE,      
                          data    = BP_MEN_Select)
# View(BP_MEN_Select)
# View(unfiltered_df)
```


## Total Respondents
```{r}
# Sum the rows of each variable included
svy_id_length <- sum(!is.na(BP_MEN_Select$svy_id))

svy_year_length <- sum(!is.na(BP_MEN_Select$svy_year))

demo_age_cat_length <- sum(!is.na(BP_MEN_Select$demo_age_cat))

demo_race_length <- sum(!is.na(BP_MEN_Select$demo_race))

demo_race_black_length <- sum(!is.na(BP_MEN_Select$demo_race_black))

demo_age_years_length <- sum(!is.na(BP_MEN_Select$demo_age_years))

demo_gender_length <- sum(!is.na(BP_MEN_Select$demo_gender))

bp_uncontrolled_accaha_length <- sum(!is.na(BP_MEN_Select$bp_uncontrolled_accaha))

htn_accaha_length <- sum(!is.na(BP_MEN_Select$htn_accaha))

cc_smoke_length <- sum(!is.na(BP_MEN_Select$cc_smoke))

cc_bmi_length <- sum(!is.na(BP_MEN_Select$cc_bmi))

cc_diabetes_length <- sum(!is.na(BP_MEN_Select$cc_diabetes))

cc_ckd_length <- sum(!is.na(BP_MEN_Select$cc_ckd))

Total_Score_length <- sum(!is.na(BP_MEN_Select$Total_Score))

Category_length <- sum(!is.na(BP_MEN_Select$Category))

Number_of_Respondents_df <- data.frame(
  Variable = c("svy_id", "svy_year", "demo_age_cat", "demo_race",
         "demo_race_black", "demo_age_years", "demo_gender", 
         "bp_uncontrolled_accaha", "htn_accaha", "cc_smoke", "cc_bmi", "cc_diabetes", "cc_ckd",
         "Total_Score", "Category"),
  Number = c(svy_id_length, svy_year_length, demo_age_cat_length, demo_race_length, demo_race_black_length,
             demo_age_years_length, demo_gender_length, bp_uncontrolled_accaha_length, htn_accaha_length,
             cc_smoke_length, cc_bmi_length, cc_diabetes_length, cc_ckd_length, Total_Score_length,
             Category_length)
)

Number_of_Respondents_df

svy_year_2013_2014 <- sum(BP_MEN_Select$svy_year == "2013-2014")

svy_year_2015_2016 <- sum(BP_MEN_Select$svy_year == "2015-2016")

svy_year_2017_2020 <- sum(BP_MEN_Select$svy_year == "2017-2020")

Number_of_Respondents_svy_year <- data.frame(
  Year = c("2013-2014", "2015-2016", "2017-2020"),
  Number = c(svy_year_2013_2014, svy_year_2015_2016, svy_year_2017_2020)
)

Number_of_Respondents_svy_year

## Smoking Status Response Rate
20608/20624

## BMI Response Rate
20062/20624
```

## Demographic Counts 
```{r}
demo_age_cat_count <- BP_MEN_Select %>%
  count(demo_age_cat)

demo_race_count <- BP_MEN_Select %>%
  count(demo_race)

demo_gender_count <- BP_MEN_Select %>%
  count(demo_gender)

demo_age_cat_count
demo_race_count
demo_gender_count
```


## Model 1: Differences in Category Per Year for htn_accaha (hypertension) and Logistic Reg Model
```{r}

ggplot(data = unfiltered_df, aes(x = Category,
                                 fill = htn_accaha)) +
  geom_bar(stat = "count", position = "fill") + 
  facet_grid(~ svy_year) +
  labs(title = "Comparison of Groups Across Categories and by Year",
       x = "Depressive Symptom Categories",
       y = "Total Number of People") +
  theme_minimal() +  
  scale_fill_manual(values = c("pink", "#67DBBD")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# ggsave("BP_MEN_minimal_htn_accaha.png", width = 8, height = 5, dpi = 300)

### Logistic Regression MOdel

BP_MEN_GLM_htn_accaha <- svyglm(htn_accaha ~ Category + svy_year, family = binomial, design = nhanesDesignUnfiltered)
summary(BP_MEN_GLM_htn_accaha)

vif(BP_MEN_GLM_htn_accaha)
```

## ORs
```{r}
exp(coef(BP_MEN_GLM_htn_accaha))
exp(cbind(OR = coef(BP_MEN_GLM_htn_accaha), confint(BP_MEN_GLM_htn_accaha)))
```



## Model 2: Differences in Depression Category Per Year for bp_uncontrolled_accaha (uncontrolled BP) and Logistic Reg Model
```{r}
ggplot(data = BP_MEN_Select, aes(x = Category,
                                 fill = bp_uncontrolled_accaha)) +
  geom_bar(stat = "count", position = "fill") + 
  facet_grid(~ svy_year) +
  labs(title = "Comparison of Groups Across Categories and by Year",
       x = "Depressive Symptom Categories",
       y = "Total Number of People") +
  theme_minimal() +  
  scale_fill_manual(values = c("pink", "#67DBBD")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

 # ggsave("BP_MEN_minimal_bp_uncontrolled_accaha.png", width = 8, height = 5, dpi = 300)

### Logistic Regression Model

BP_MEN_GLM_bp_uncontrolled_accaha <- svyglm(bp_uncontrolled_accaha ~ Category + svy_year, design = nhanesDesignSelect, family = binomial)
summary(BP_MEN_GLM_bp_uncontrolled_accaha)

vif(BP_MEN_GLM_bp_uncontrolled_accaha)
```


## ORs
```{r}
exp(coef(BP_MEN_GLM_bp_uncontrolled_accaha))
exp(cbind(OR = coef(BP_MEN_GLM_bp_uncontrolled_accaha), confint(BP_MEN_GLM_bp_uncontrolled_accaha)))
```

### Model 3: Multiple Logistic Regression model for bp_uncontrolled_accaha ~ All Demographic Variables and Comorbidities
```{r}

BP_MEN_GLM_bp_uncontrolled_multiple <- svyglm(bp_uncontrolled_accaha ~ Category + svy_year + demo_age_cat + demo_gender + demo_race + cc_bmi + cc_diabetes + cc_ckd + cc_smoke, design = nhanesDesignSelect, family = binomial) #added cc_smoke and demo_race as of march 19
summary(BP_MEN_GLM_bp_uncontrolled_multiple)

vif(BP_MEN_GLM_bp_uncontrolled_multiple)
```

## ORs
```{r}
exp(coef(BP_MEN_GLM_bp_uncontrolled_multiple))
exp(cbind(OR = coef(BP_MEN_GLM_bp_uncontrolled_multiple), confint(BP_MEN_GLM_bp_uncontrolled_multiple)))
```


## Model 4: Multiple Logistic Regression model for Uncontrolled BP  ~  Depression Category and Antidepressant Use, Fitted With an Interaction Term to Determine if Antidepressant Use is an EMM
```{r}
model4 <- svyglm(bp_uncontrolled_accaha ~ svy_year + Category + Antidepressant_Y_N + Category*Antidepressant_Y_N, design = nhanesDesignSelect, family = binomial) #added svy_year as of march 19
summary(model4)

vif(model4)
model4_test <- svyglm(bp_uncontrolled_accaha ~ Category + Antidepressant_Y_N + Category*Antidepressant_Y_N, design = nhanesDesignSelect, family = binomial)

vif(model4_test)
```

## ORs
```{r}
exp(coef(model4))
exp(cbind(OR = coef(model4), confint(model4)))
```


## Demographic Variable Exploration

+ The other variables will be explored with both the htn_accaha and the bp_uncontrolled_accaha

### Facet Wrap By demo_age_cat

```{r}
ggplot(data = BP_MEN_Select, aes(x = Category,
                                 fill = bp_uncontrolled_accaha)) +
  geom_bar(stat = "count", position = "dodge") + 
  facet_grid(~ svy_year) +
  labs(title = "Comparison of Groups Across Categories and by Year",
       x = "Depressive Symptom Categories",
       y = "Total Number of People") +
  theme_minimal() +  
  scale_fill_manual(values = c("blue", "red")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ demo_age_cat) 

### Logistic Regression Model

#bp_uncontrolled_accaha

BP_MEN_GLM_bp_uncontrolled_accaha_demo_age_cat <- svyglm(bp_uncontrolled_accaha ~ Category + svy_year + demo_age_cat, design = nhanesDesignSelect, family = binomial)
summary(BP_MEN_GLM_bp_uncontrolled_accaha_demo_age_cat)

```

### Facet Wrap By demo_gender

```{r}
ggplot(data = BP_MEN_Select, aes(x = Category,
                                 fill = bp_uncontrolled_accaha)) +
  geom_bar(stat = "count", position = "dodge") + 
  facet_grid(~ svy_year) +
  labs(title = "Comparison of Groups Across Categories and by Year",
       x = "Depressive Symptom Categories",
       y = "Total Number of People") +
  theme_minimal() +  
  scale_fill_manual(values = c("blue", "red")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ demo_gender) 

### Logistic Regression Model

#bp_uncontrolled_accaha

BP_MEN_GLM_bp_uncontrolled_accaha_demo_gender <- svyglm(bp_uncontrolled_accaha ~ Category + svy_year + demo_gender, design = nhanesDesignSelect, family = binomial)
summary(BP_MEN_GLM_bp_uncontrolled_accaha_demo_gender)
```

### Facet Wrap By cc_bmi

```{r}
ggplot(data = BP_MEN_Select, aes(x = Category,
                                 fill = bp_uncontrolled_accaha)) +
  geom_bar(stat = "count", position = "dodge") + 
  facet_grid(~ svy_year) +
  labs(title = "Comparison of Groups Across Categories and by Year",
       x = "Depressive Symptom Categories",
       y = "Total Number of People") +
  theme_minimal() +  
  scale_fill_manual(values = c("blue", "red")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ cc_bmi) 


### Logistic Regression Model

BP_MEN_GLM_htn_accaha_cc_bmi <- svyglm(bp_uncontrolled_accaha ~ Category + svy_year + cc_bmi, design = nhanesDesignSelect, family = binomial)
summary(BP_MEN_GLM_htn_accaha_cc_bmi)



```

### Facet Wrap By cc_diabetes

```{r}
ggplot(data = BP_MEN_Select, aes(x = Category,
                                 fill = bp_uncontrolled_accaha)) +
  geom_bar(stat = "count", position = "dodge") + 
  facet_grid(~ svy_year) +
  labs(title = "Comparison of Groups Across Categories and by Year",
       x = "Depressive Symptom Categories",
       y = "Total Number of People") +
  theme_minimal() +  
  scale_fill_manual(values = c("blue", "red")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ cc_diabetes) 

### Logistic Regression Model

#bp_uncontrolled_accaha

BP_MEN_GLM_bp_uncontrolled_accaha_cc_diabetes <- svyglm(bp_uncontrolled_accaha ~ Category + svy_year + cc_diabetes, design = nhanesDesignSelect, family = binomial)
summary(BP_MEN_GLM_bp_uncontrolled_accaha_cc_diabetes)

```

### Facet Wrap By cc_ckd

```{r}
ggplot(data = BP_MEN_Select, aes(x = Category,
                                 fill = bp_uncontrolled_accaha)) +
  geom_bar(stat = "count", position = "dodge") + 
  facet_grid(~ svy_year) +
  labs(title = "Comparison of Groups Across Categories and by Year",
       x = "Depressive Symptom Categories",
       y = "Total Number of People") +
  theme_minimal() +  
  scale_fill_manual(values = c("blue", "red")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ cc_ckd) 


### Logistic Regression Model


#bp_uncontrolled_accaha

BP_MEN_GLM_bp_uncontrolled_accaha_cc_ckd <- svyglm(bp_uncontrolled_accaha ~ Category + svy_year + cc_ckd, design = nhanesDesignSelect, family = binomial)
summary(BP_MEN_GLM_bp_uncontrolled_accaha_cc_ckd)

```




